### 2014-07-09 paper/introduction.tex
final tweaks for 1AC to check accepted submission

\changes{This paper introduces a novel tool that provides path planning and other high-level functionality to support the design of interior pipes and cavities within 3D models.  These pipes can be filled, post-print, with a variety of media to enable input, display, and tactile feedback.}  This {\em subtractive} approach is complementary to {\em additive} approaches that inject custom print materials, such as conductors, during the actual printing process \cite{Sells-reprap}. While our approach requires some manual assembly after a print completes, it gives makers the opportunity to cheaply and rapidly prototype a range of interactive objects on 3D printers, including popular single-material fused-deposition modeling machines (colored objects in Figure \ref{fig:teaser}).  \changes{Additionally, once printers able to deposit conductive materials become commercially available, PipeDream will still support the internal 3D modeling tasks required for directly printing different materials.}

>>>>

\changes{This paper introduces a novel tool that provides path planning and other high-level functionality to support the design of interior pipes and cavities within 3D models.  These pipes can be filled, post-print, with a variety of media to enable input, display, and tactile feedback.}  This {\em subtractive} approach is complementary to {\em additive} approaches that inject custom print materials, such as conductors, during the actual printing process \cite{Sells-reprap}. While our approach requires some manual assembly after a print completes, it gives makers the opportunity to cheaply and rapidly prototype a range of interactive objects on 3D printers, including popular single-material fused-deposition modeling machines (colored objects in Figure \ref{fig:teaser}).  \changes{Our software contributions can also provide useful modeling capabilities for future multi-material printers, e.g., printers that that are able to deposit conductive materials directly, without manual assembly.}

### 2014-07-09 paper/tubes.tex
final tweaks for 1AC to check accepted submission

The wire is modelled as a \emph{discrete rod}: a 3D poly-line with a bending 
constraint between adjacent segments. Our simulation is based on an
implementation of Position-Based Dynamics (PBD)~\cite{Muller07}, with all constraints
modelled as penalty forces. To keep the rod inside the
mesh, we compute a discretized distance field, then constrain the
rod to stay within our offset shell using a simple penalty force.

@@

PBD simulations rarely converge to a steady state, so we simply halt after a fixed number of timesteps (250). Our voxel grid currently uses a resolution of 128x128x128 voxels, which enables interactive operations, but this parameter can be adjusted for different model requirements. The simulation takes about a second for our examples, including those in Figure \ref{fig:complex}.

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/routing-tests.png}
\caption{\changes{A set of example routings produced by our tool.  Note that there is a tradeoff between bending and length of pipes: our pipes prefer shortness, however pipes could "jump around" holes in genus $> 0$ meshes (a) to reduce bending.  Pipes successfully route through long, curving paths in knots (b), and multiple pipes placed in a single mesh in a tangled configuration successfully avoid each other (c).}}
\label{fig:complex}
\end{figure}

\subsubsection{Multiple Pipes}
Pipes are routed and cut out of the mesh serially. This prevents pipe intersections: once a pipe has been cut out of the mesh, it cannot be part of valid routes in any future pipe routing operation. After solving for a path, we add it as a constraint to the system, generating
a penalty force that pushes additional paths away from it.  However, we do not currently track all pipes for global optimization: we greedily select the best routing per pipe.

@@

\subsection{Model Assembly}
For especially complex geometries, models can be ``cut up'' into multiple pieces that can be assembled, avoiding support deposition or easing material removal; this can also ease insertion of the desired medium. This is somewhat undesirable as it means more time spent in assembly post-print, and additionally a cut pipe may no longer be fluid-tight.  Our plane cut option goes towards this, however a more advanced tool for this purpose is outside the scope of this work.
}

>>>>

The wire is modelled as a \emph{discrete rod}: a 3D poly-line with a bending 
constraint between adjacent segments. Our simulation is based on an
implementation of Position-Based Dynamics (PBD)~\cite{Muller07}, with all constraints
modelled as penalty forces. To keep the rod inside the
mesh, we compute a discretized distance field, then constrain the
rod to stay within our offset shell using a simple penalty force. \changes{This approach can successfully route pipes through complex geometries (Figure \ref{fig:complex}).}

@@

PBD simulations rarely converge to a steady state, so we simply halt after a fixed number of timesteps (250). Our voxel grid currently uses a resolution of 128x128x128 voxels, which enables interactive operations, but this parameter can be adjusted for different model requirements. The simulation takes about a second for our examples.

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/routing-tests.png}
\caption{\changes{A set of example routings produced by our tool.  Note that there is a tradeoff between bending and length of pipes: to reduce bending, pipes may be routed through longer paths around holes in genus $> 0$ meshes (a).  Pipes successfully route through long, curving paths in knots (b), and multiple pipes placed in a single mesh in a tangled configuration successfully avoid each other (c).}}
\label{fig:complex}
\end{figure}

\subsubsection{Multiple Pipes}
Pipes are routed and cut out of the mesh serially. \changes{This prevents pipe intersections: once a pipe has been cut out of the mesh, it cannot be part of valid routes in any future pipe routing operation (Figure~\ref{fig:complex}c)}. After solving for a path, we add it as a constraint to the system, generating
a penalty force that pushes additional paths away from it.  However, we do not currently track all pipes for global optimization: we greedily select the best routing per pipe.

@@

\subsection{Model Assembly}
For especially complex geometries, models can be ``cut up'' into multiple pieces that can be assembled, avoiding support deposition or easing material removal; this can also ease insertion of the desired medium. This is somewhat undesirable as it means more time spent in assembly post-print, and additionally a cut pipe may no longer be fluid-tight.  
%Our plane cut option goes towards this, however a more advanced tool for this purpose is outside the scope of this work.
Our plane cut option offers a simple way to slice a model; more sophisticated techniques may be necessary for internal paths that are not constrained to a plane.
}
